Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-26 Thesis/chapter/07-outlook.tex
start outlook

@@

It should have been alos verglichen with grid search with comparable size
but most time was used to find a vernuenfig base recipe and process

>>>>

\todo{freewriting:} 
what did i want to do? 
The goal of this work was to find a sol-gel process resulting in a insulating zirconium ceramic on top of steel.
This aufbau then can be used for thin layer photo voltaics. 
The ceramic needs to be homoegeneous and defect free. 
what was done? 
A suitable recipe was found and optimized via \gls{emma}. 
welche methoden wurden dafür verwendet? 
after the optimsation the data was analysed with further/different machine learning methods like kernel ridge regression, support vector regression and linear regression. 
was wurde herausgefunden? 
A strong correlation of calcination temperature and conductance in the bereich of 300--400\oc{}. 
was kann noch herausgefundne werden und wie?

was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd

@@

It should have been also verglichen with grid search with comparable size
but most time was used to find a vernuenfig base recipe and process
